Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 payment-proof.tex
find an error, but not sure how to fix it
proposed change to lemma 14

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
\end{align}
\end{rtheorem}

@@

Next, we show that for any sample path \SP in the envelope \Env{\ell},
we can bound the total number of payments made in terms of $\ell$.
Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
happens.
Because $s \geq h(\ell)$, we get that
$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
as well as $s \geq \exp(2/\MinProb)$.
Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
that the pull at time $t$ was not incentivized.
\end{proof}

@@

\dkcomment{Did we forget a sum over \SP here?}

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp\left(\frac{2}{\MinProb}\right) \right).  \nonumber 
\end{align}
\end{rtheorem}

@@

Next, we show that for any sample path \SP in the envelope \Env{\ell},
we can bound the total number of payments made in terms of $\ell$.
Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
\pfedit{
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
}
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

@@

\begin{proof}
The proof is similar to that of Lemma~\ref{lem:numP}.
Fix a sample path $\SP \in \Env{\ell}$.
Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
happens.
Because $s \geq h(\ell)$, we get that
$g(s,\ell) \leq \pfedit{\min(\frac{\TieCutoff}{2\Diam d},} \frac{\MinProb}{4 \Diam d \TieDensity}\pfedit{)}$
as well as $s \geq \exp(2/\MinProb)$.
Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
that the pull at time $t$ was not incentivized.
\end{proof}

@@
